TBD

### 2020-11-07 Articles/2020-ClassicalMechanicsPhil/Source/classical-phil-article.tex
Update classical-phil-article.tex

\item motivate everything upfront: going to show that Hamiltonian mechanics corresponds to three conditions being satisfied, while Lagrangian mechanics requires a fourth condition
\item define the three assumptions, and give motivation
\item figuring out which mathematical structures are required for systems that satisfy certain physical conditions
\item go over the upshot of the philosophical argument, specifically how this avoids the worries about measuring the amount of structure that plagued North (i.e. Swanson and Halvorson paper)
\item Then, give the derivation, as gentle and well-motivated as possible. But would be ideal if readers could skip or skim this section and still get the philosophical upshot, relatively early on.

>>>>

\item motivate everything upfront: going to show that Hamiltonian mechanics corresponds to two conditions being satisfied, while Lagrangian mechanics requires a three condition
\item define the two assumptions, and give motivation
\item figuring out which mathematical structures are required for systems that satisfy certain physical conditions
\item go over the upshot of the philosophical argument, specifically how this avoids the worries about measuring the amount of structure that plagued North (i.e. Swanson and Halvorson paper)
\item Then, give the derivation, as gentle and well-motivated as possible. But would be ideal if readers could skip or skim this section and still get the philosophical upshot, relatively early on.
